Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-11 article.tex
searches and .bibs

@@

@@

\subsection{Sustainability in Coonawarra Winegrowing: Key Factors and Influences}
        Sustainability in Coonawarra Winegrowing: Key Factors and Influences
    How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
        Purpose: Examine regional differences and tailor sustainability strategies.
        Results: Compare the generic model to the Coonawarra model. Acknowledge there is more work to be done here due to the amount of regions across Australia and the world. Prevous work also helps to illustrate these differences.

    How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?
        Purpose: Assess different factors overall influence to environmental sustainability given the definitions used.
        Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects environmental sustainability.

Structuring the Results Section Based on These Questions:
Introduction to Results

>>>>

Table of definitions

@@

Leximancer figure

@@

Figure of General model

\subsection{Sustainability specifics: Coonawarra Winegrowing}
        Sustainability in Coonawarra Winegrowing: Key Factors and Influences
    #TODO: what are the regional specifics of coonawarra
    How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
        Purpose: Examine regional differences and tailor sustainability strategies.
        Results: Compare the generic model to the Coonawarra model. Acknowledge there is more work to be done here due to the amount of regions across Australia and the world. Prevous work also helps to illustrate these differences.

    How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in Coonawarra?
        Purpose: Assess different factors overall influence to environmental sustainability given the definitions used.
        Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects environmental sustainability.

Figure Marcel + robyn BNs

% =================================
Structuring the Results Section Based on These Questions:
Introduction to Results
